%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj; MOdified by Vishnu Easwaran E for personal use.
% License : MIT
%------------------------

\documentclass[a4paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}

\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,urlcolor=linkcolour}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.475in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.3in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Vishnu Easwaran E} & Email : \href{mailto:easwaranvishnu@gmail.com}{easwaranvishnu@gmail.com}\\
  \href{https://github.com/vishnueaswaran}{GitHub} \& \href{https://www.linkedin.com/in/vishnueaswaran/}{LinkedIn} & Mobile : +91-xxxxxxxxxx
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sree Chitra Thirunal College of Engineering; University of Kerala}{Kerala, India}
      {Bachelor of Technology in Electronics and Communication}{Aug. 2010 -- April 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Free/Libre and Open Source Software for Education--- FOSSEE, IIT Bombay}{Mumbai, India}
      {Research Associate}{July 2017 - Present}

      \resumeItemListStart
        \resumeItem{OpenPLC}
          {Development of IEC61131-3 and IEC61499 standard PLCs for educational purposes.}

          \resumeItemListStart
	          \resumeItem{Hardware/Electronics Design}
              {PCB design, layout, prototyping and testing. Designed power management, communication, ADC and interfacing elements.}
            \resumeItem{Embedded Software/Firmware}
	            {Developed Firmware for controllers, application software and scripts for Linux running in single board computers. Built bespoke Linux images from source using Yocto.}
            \resumeItem{System Design}
              {Logical design, Physical design, Architectural design, and analysis of PLC system complying with the IEC 61131-3 \& 61499 standards.}
	        \resumeItemListEnd

          \resumeItem{Documentation}
            {Managed the creation of tutorials for OpenPLC and its sister hardware projects, in the SpokenTutorial platform of Government of India.}
          \resumeItem{Teachers Training}
            {Lead a team of 6 in conducting technical workshops on behalf of FOSSEE, for faculties and students, in engineering and polytechnic colleges.}
          \resumeItem{Mentor}
            {Identification, selection and mentoring of FOSSEE summer fellows from all over India.}
        \resumeItemListEnd

    \resumeSubheading
      {FabLab Kerala--- KSUM, Govt. of Kerala.}{Kerala, India}
      {Technical Associate}{December 2016 - July 2017}

      \resumeItemListStart
        \resumeItem{Technical Associate}
          {Technical associate to artists of Kochi Muziris Biennale on behalf of KSUM.}
        \resumeItem{Fab Academy Instructor}
          {Course instructor and evaluator at Trivandrum Fab Lab for the batch of 2017.}
        \resumeItem{Mini-FabLabs}
          {Setup mini-fablabs in association with Fab Foundation, across the state.}
      \resumeItemListEnd

    \resumeSubheading
      {Kerala Startup Mission--- KSUM, Govt. of Kerala.}{Kerala, India}
      {Technology Innovation Fellow}{June 2015 - June 2016}

      \resumeItemListStart
        \resumeItem{Fab Lab}
          {Setup Fab Labs in Trivandrum and Kochi. Developed and mentored research projects at Fab Labs.}
        \resumeItem{Technical Consultant}
          {Rapid prototyping consultant at Fab Lab for start-ups, engineering colleges, NGOs etc.}
        \resumeItem{State Policy Agent}
          {Implementation and monitoring of entrepreneurship development programs of Kerala State government's startup policy.}
      \resumeItemListEnd

    \resumeSubheading
      {Sahridhaya--- NGO}{Kerala, India}
      {Trustee}{June 2012 - Present}

      \resumeItemListStart
        \resumeItem{Head of R\&D}
          {Developed various educational tools and programs for teaching STEM among school students. Organized and volunteered for numerous social activities in the state, latest during the devastating Kerala floods.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{PROTON}
      {An Arduino based development board with a battery of on-board sensors and actuators bundled with provisions for multiple communication technologies.}
    \resumeSubItem{CoW-Net}
      {A research project that deployed an open-wireless network in a Panchayat connecting the local populace with modern tech-enabled services like instant messaging, geo-tagging, educational content portals etc.}
    \resumeSubItem{S\textsuperscript{2} - Smart Switch}
      {An IOT enabled power-switch which can be controlled over internet.}
    \resumeSubItem{Hypothermia detector}
      {A functional prototype, with a system made of an Attiny 45 and an NTC thermostat.}
    \resumeSubItem{Mind Controlled Wheelchair}
      {Proof-of-concept of an EEG controlled wheelchair for individuals with limited motor abilities.}
  \resumeSubHeadingListEnd

% --------CERTIFICATES & REWARDS------------
\section{Certificates and Awards}
  \resumeSubHeadingListStart
    \resumeSubItem{Management Development Program}{IIM Kozhikode - 2016}
    \resumeSubItem{Fab Academy Diploma in Digital Fabrication}{Fab Foundation - 2016}
    \resumeSubItem{Manorama Yuva Master Mind}{Malayala Manorama - 2012}
  \resumeSubHeadingListEnd

% --------PUBLICATIONS------------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{``Programmable Logic Controller: Open Source
Hardware and Software for Massive Training" at IECON'18, Washinton D.C, USA }{2018} \href{https://ieeexplore.ieee.org/abstract/document/8592772/}{| LINK}
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Design and Engineering Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Embedded C, Arduino, C/C++}
     \hfill
     \textbf{Technologies}{: EDA, ARM, Linux, Yocto, RaspberryPi, STM Boards}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

